CF-SuGAR Power Calculations

### 2025-03-21 Christine Chan/CF-SuGAR/power_calculations.qmd
aim2 power for Deb

```{r}
registry$bmi[registry$bmi >= 200] <- NA
# Write for SAS
write.csv(registry,
  file = "./CF-SuGAR/Background/Power Calculations/Data/registry.csv",
  row.names = F, na = ""
)
```

@@

```{r}
mod1 <- lmer(bmi ~ Age_YrEnd + (1 | eDWID), data = registry)
summary(mod1,ddf="Kenward-Roger")
```

>>>>

```{r}
registry$bmi[registry$bmi >= 200] <- NA
# A1c group
registry$a1c_group <- cut(registry$A_hgba1c, c(-Inf, 5.9, Inf))
# Remove people with CFRD
registry <- registry %>% filter(CFRD != "CFRD+")
# Write for SAS
write.csv(registry,
  file = "./CF-SuGAR/Background/Power Calculations/Data/registry.csv",
  row.names = F, na = ""
)
```

@@

```{r}
mod1 <- lmer(bmi ~ Age_YrEnd + (1 | eDWID), data = registry)
summary(mod1, ddf = "Kenward-Roger")
```
